On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-01-14 paper_lap/01intro.tex
updating manuscript

 The paper is organized as follows. In~\cref{sec:mprelim} we review relevant mathematical results associated with Laplace's equation. ~\cref{sec:bvp} describes the reduction of boundary value problems to boundary integral equations via potential theory, and reviews the analytic behavior of solutions near a corner. In~\cref{sec:nprelim,sec:napp} we present our numerical algorithm and the associated analysis. Finally, in~\cref{sec:num} we illustrate its application with several numerical experiments.

>>>>

 The paper is organized as follows. In~\cref{sec:mprelim} we review relevant mathematical results associated with Laplace's equation.~\cref{sec:bvp} describes the reduction of boundary value problems to boundary integral equations via potential theory, and reviews the analytic behavior of solutions near a corner. In~\cref{sec:nprelim,sec:napp} we present our numerical algorithm and the associated analysis. Finally, in~\cref{sec:num} we illustrate its application with several numerical experiments.

### 2020-01-14 paper_lap/06num.tex
updating manuscript

After re-solving the density, we also compute the solution at target locations on a tensor product polar grid, where the grid
is exponentially spaced in the radial direction and equispaced in the angular direction. For target locations
close to panels which are not at the corner, we use adaptive integration in order to resolve the near-singular behavior of
the kernel for accurate computation of the integrals. For target locations close to the corner panel, since we do not have
the capability to interpolate the density, we use the underlying smooth quadrature rules for computing their contribution. 
The reference solution and the errors are demonstrated in~\cref{fig:vol-plot}.
\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{media/volume}
\caption{Top row: Solution on the volume after 10, 20, and 40 iterations of resolve. The target locations are a tensor product polar grid, where the nodes are exponentially spaced in the radial direction. The closest target location is approximately $10^{-13}$ away from the corner. Near quadrature is handled via adaptive integration except for the corner panel where the smooth quadrature weights are used. Bottom row: analogous results where the solution is computed using a graded mesh.   }.
\label{fig:vol-plot}
\end{center}
\end{figure}

\subsection{Performance}
In this section, we demonstrate the performance of the solver by solving a scattering problem in the
exterior of a ``broken wheel'' region. The boundary data is given by
\begin{equation}
f(x) = \nabla  \sum_{j=1}^{57} c_{j} \log| \bx - \bx_{j}| \cdot \bnu(\bx) \, , 
\end{equation}
where there is one $\bx_{j}$ located in each of the spokes, one of the $\bx_{j}$ is in the central disc, and the remaining $50$ $\bx_{j}$ are chosen randomly in the exrterior of the bounding disc containing the domain. The strengths $c_{j}$ are chosen such that they average to $0$. The domain contains $108$ corners, was discretized using $22240$ nodes and required $105$ iterations to converge to a residue of $10^{-15}$. The matrix at each iteration was applied using an FMM whose tolerance was also set to $10^{-15}$. The solution was computed in $15$ secs, and plotted at a $500\times 500$ grid of targets in $6.5$ secs. All of the results have been computed on a single core on a Macintosh machine with Intel core i5 2.3GHz processors. In~\cref{fig:magnetron}, we plot the scattered field, the right hand side, and the computed density.

>>>>

After re-solving the density, the solution is evaluated on a tensor product polar grid, where the grid
is exponentially spaced in the radial direction and equispaced in the angular direction. For evaluation points (targets)
close to panels which are not at the corner, we use adaptive integration in order to resolve the near-singular behavior of
the kernel for accurate computation of the integrals. For target locations close to the corner panel, since we do not have
the capability to interpolate the density, we use the underlying smooth quadrature rules for computing their contribution. 
The reference solution and the errors are demonstrated in~\cref{fig:vol-plot}.
\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{media/volume}
\caption{Top row: Solution on the volume after 10, 20, and 40 iterations of re-solve. The solution is computed on a tensor product polar grid, where the evaluation points (targets) are exponentially spaced in the radial direction. The closest target location is approximately $10^{-13}$ away from the corner. Near quadrature is handled via adaptive integration except for the corner panel where the smooth quadrature weights are used. Bottom row: analogous results where the solution is computed using a graded mesh.   }.
\label{fig:vol-plot}
\end{center}
\end{figure}

\subsection{Performance}
In this section, we demonstrate the performance of the solver by solving a scattering problem in the
exterior of a ``broken wheel'' region. The boundary data is given by
\begin{equation}
f(x) = \nabla  \sum_{j=1}^{57} c_{j} \log| \bx - \bx_{j}| \cdot \bnu(\bx) \, , 
\end{equation}
where there is one $\bx_{j}$ located in each of the spokes, one of the $\bx_{j}$ is in the central disc, and the remaining $50$ $\bx_{j}$ are chosen randomly in the exrterior of the bounding disc containing the domain. The strengths $c_{j}$ are chosen such that they average to $0$. The domain contains $108$ corners, was discretized using $22240$ nodes and required $105$ iterations to converge to a residue of $10^{-15}$. The matrix at each iteration was applied using an FMM whose tolerance was also set to $10^{-15}$. The solution was computed in $15$ secs, and plotted at a $500\times 500$ grid of targets in $6.5$ secs. All of the results have been computed on a single core on a Macintosh machine with Intel core i5 2.3GHz processors. In~\cref{fig:magnetron}, we plot the scattered field, the boundary data, and the computed density.

### 2020-01-14 paper_lap/manuscript.tex
updating manuscript

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
In this section, we demonstrate that for a panel which is sufficiently far from the corner and  discretized using $M$ Gauss-Legendre nodes, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]$ denote an arc-length parameterization of the boundary.
Let $\gamma([s_{1},s_{2}])$ be a panel discretized using $M$ Gauss-Legendre nodes be such that if $r_{0}$ denotes
the distance to the closest corner on the particular edge, the length of the panel $L_{0}<r_{0}/2$, i.e. the panel
is separated from the nearest corner by at least two times its own length. Further assume that no point on the boundary $\Gamma$ which is not on the same edge as as $\gamma([s_{1},s_{2}])$ is contained in some $\rho-$Bernstein ellipse
corresponding to the line segment $\gamma([s_{1},s_{2}])$ with $\rho>1$. Furthermore suppose that all of the panels away from the corner and not on the edge containing the segment $\gamma([s_{1},s_{2}])$ are such that any point on $\gamma([s_{1},s_{2}])$ is not contained in their $\rho-$ Bernstein ellipse.
Both of these assumptions can always be met by choosing sufficiently small panels away from the corners. Finally 
assume that all panels at any corner $r_{c}$ are such that any point on $\gamma([s_{1},s_{2}])$ is at least $2r_{c}$ 
away from the corner vertex. Under all of these assumptions, it can be shown that the accuracy in computing the
Legendre coefficients of the density corresponding to the Neumann problem, is the same as the accuracy
of a related Dirichlet problem where the boundary data is resolved with controlled error on the given discretization.

Let $A$ denote the operator corresponding to interior Dirichlet problem using a double layer potential. Let $g$ denote the
right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution. Let $f$ be a Legendre polynomial of
degree $n$ scaled to the panel $\gamma_{[s_{1},s_{2}]}$ and $0$ everywhere else. Then
\begin{equation}
\left<\sigma, f \right> = \left< (A^{T})^{-1} g, f\right> = \left< g, A^{-1} f \right> = \langle g, \sigma_{f}\rangle \, ,
\end{equation}
where $\sigma_{f}$ is the solution of the interior Dirichlet problem with boundary data $f$ using a double layer potential.

@@

For any $s$ which is contained on the same segment as $\gamma_{[s_{1},s_{2}]}$, the kernel $k(s,t)$ is identically $0$.
Thus the boundary data $\tilde{f}(s)=0$  on the same edge as the panel $\gamma([s_{1},s_{2}])$. 
We further observe that $f(t)$ is an entire function when extended to the complex plane (since it is a Legendre polynomial)
and the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is corresponding to $\gamma(s)$.
Since we have assumed that no other point on the boundary $\Gamma$ is contained in the $\rho-$ bernstein ellipse
of the panel $\gamma[(s_{1},s_{2})]$, 
the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho^{-M}$, where
the constant $C$ is related to the boundedness of the function $k(s,t)$ when $t$ is complexified.
(Note the error is not $\rho^{-2M}$ since $P_{M}$ would grow like $\rho^{M}$ on the $\rho-$ Bernstein ellipse.) 
Thus the function $\tilde{f}(s)$ can be computed to any desired precision by increasing the order of quadrature nodes
used to compute the integrals.

With regards to the resolution of the of the function $\tilde{f}(s)$ on the given discretization of the boundary, 
we note that the closest singularity of the function $\tilde{f}(s)$ when restricted to a panel away from the corner
and not on the same edge as $\gamma([s_{1},s_{2}])$ is the closest point on the panel $\gamma([s_{1},s_{2}])$. 
However, since we have assumed that all panels away from corners are such that no point on $\gamma([s_{1},s_{2}])$ 
is contained in their $\rho-$ Bernstein ellipse, the error in resolving the function $\tilde{f}(s)$ using an $M$ point Gauss-Legendre
or Chebyshev panel is bounded by $C \rho^{-M}$. Note that the behavior of $\tilde{f}(s)$ in the complex plane is related
to the behavior of $k(s,t)$ in the complex $s$ plane and hence can be made $O(1)$.
For the panels, at the corner, based on the proof in Appendix A, the error in resolving the function $\tilde{f}(s)$ when
truncated to a taylor series of order $N$ is less than $C 2^{-N}$, since all points on $\gamma([s_{1},s_{2}])$ are 
well-separated from corners by twice the panel length $r_{c}$. Thus, by making the panels small enough, $\rho$ can be increased arbitrarily to obtain desired tolerances on the boundary data $\tilde{f}(s)$ on the corresponding discretization of the boundary.

>>>>

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
In this section, we demonstrate that for a panel which is sufficiently far from the corner and  discretized using $M$ Gauss-Legendre nodes, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]$ denote an arc-length parameterization of the boundary.
Assume that the discretization satisfies the following assumptions:
\begin{enumerate}
\item All panels which are not at a corner, are separated from the closest corner by their panel length.
\item Let $E_{\rho}(\Gamma_{i})$ denote the Bernstein $\rho-$ellipse corresponding to panel $\Gamma_{i}$, and let $\rho_{i}$ 
be such that $E_{\rho_{i}}(\Gamma_{i})$ does not intersect $\Gamma \setminus S_{\Gamma_{i}}$, where 
$S_{\Gamma_{i}}$ is the edge containing $\Gamma_{i}$ (see~\cref{fig:illus-cons}). Let $\rho_{0} = \min_{i} \rho_{i} >1$.
\item All panels which are not adjacent to a panel at the corner, are separated from the corner by $2r_{c}$ where $r_{c}$ 
denotes the length of the panel at the corner.
\end{enumerate}
Under these assumptions, it can be shown that the accuracy in computing the
Legendre coefficients of the density (at panels which are not adjacent to a corner panel) for the Neumann problem, is related to the accuracy 
of a Dirichlet problem where the boundary data is resolved with controlled error on the given discretization.
\begin{figure}
\begin{center}
\includegraphics[width=0.3\linewidth]{media/geom-restriction-illus}
\caption{Illustrative figure for demonstrating constraints required on the geometry discretization. The panel $\Gamma_{i}$ satisfies restriction 1 if $L_{i}/L_{0}>1$. Panel $\Gamma_{j}$ illustrates the largest Bernstein ellipse which intersects the other edges, and Panel $\Gamma_{k}$ illustrates restriction 3 if $r_{k}>2r_{c}$. }
\label{fig:illus-cons}
\end{center}
\end{figure}

Let $A$ denote the operator corresponding to interior Dirichlet problem using a double layer potential. Let $g$ denote the
right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution. Let $f$ be a Legendre polynomial of
degree $n$ scaled to the panel $\gamma([s_{1},s_{2}])$ and $0$ everywhere else. Then
\begin{equation}
\left<\sigma, f \right> = \left< (A^{T})^{-1} g, f\right> = \left< g, A^{-1} f \right> = \langle g, \sigma_{f}\rangle \, ,
\end{equation}
where $\sigma_{f}$ is the solution of the interior Dirichlet problem with boundary data $f$ using a double layer potential.

@@

For any $s$ which is contained on the same segment as $\gamma_{[s_{1},s_{2}]}$, the kernel $k(s,t)$ is identically $0$.
Thus the boundary data $\tilde{f}(s)=0$  on the same edge as the panel $\gamma([s_{1},s_{2}])$. 
We further observe that $f(t)$ is an entire function when extended to the complex plane (since it is a Legendre polynomial)
and the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is corresponding to $\gamma(s)$.
From assumption 2, it follows that
the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho_{0}^{-M}$, where
the constant $C$ is related to the boundedness of the function $k(s,t)$ when $t$ is complexified.
(Note the error is not $\rho_{0}^{-2M}$ since $P_{M}$ would grow like $\rho_{0}^{M}$ on the $\rho_{0}-$ Bernstein ellipse.) 
Thus the function $\tilde{f}(s)$ can be computed to any desired precision by increasing the order of quadrature nodes
used to compute the integrals.

With regards to the resolution of the of the function $\tilde{f}(s)$ on the given discretization of the boundary, 
we note that the closest singularity of the function $\tilde{f}(s)$ when restricted to a panel away from the corner
and not on the same edge as $\gamma([s_{1},s_{2}])$ is the closest point on the panel $\gamma([s_{1},s_{2}])$. 
However, by assumption 2, the error in resolving the function $\tilde{f}(s)$ using an $M$ point Gauss-Legendre
or Chebyshev panel is bounded by $C \rho_{0}^{-M}$. Note that the behavior of $\tilde{f}(s)$ in the complex plane is related
to the behavior of $k(s,t)$ in the complex $s$ plane and hence the constant $C$ is $O(1)$.
For the panels, at the corner, based on the proof in Appendix A, the error in resolving the function $\tilde{f}(s)$ when
truncated to a taylor series of order $N$ is less than $C 2^{-N}$, since all points on $\gamma([s_{1},s_{2}])$ are 
well-separated from corners by twice the panel length $r_{c}$. Thus, by making the panels small enough, $\rho$ can be increased arbitrarily to obtain desired tolerances on the boundary data $\tilde{f}(s)$ on the corresponding discretization of the boundary.
